Papers

### 2023-12-15 papers.qmd
add paper
add JAP paper

## 2023
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, accepted 2023.

>>>>

## 2023
R. Darling, G. S. Clark, and **J. D. Tucker**, "Hidden Ancestor Graphs: Models for Detagging Property Graphs", *arXiv:2102.09581 [math.PR]*. 2023 [arxiv preprint](https://arxiv.org/abs/2102.09581)

A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, vol. 134, no. 23, 2023. [PDF](Papers/JAP23_calibration.pdf)
